---
#title: "GSB 503 Industry Project"
#author: "Max Sohl"
#subtitle: 'Modeling Group 3: SPP'
output: ioslides_presentation
widescreen: true
#output: revealjs::revealjs_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE)
library(revealjs)
library(knitr)
library(DT)
library(tidyverse)
library(readr)
library(ggmap)
library(dplyr)
library(sf)
library(nngeo)
library(tidyr)
library(usdata)
library(leaflet)
library(geosphere)
library(sp)

#DATA Load + Clean for map
NO_GEOMETRY <- read.csv("final_Data_No_Geometry.csv")

final_data <- NO_GEOMETRY
# %>% create with control shift m

final_data <- final_data %>%
  mutate(dist = distHaversine(cbind(Generator_Longitude, Generator_Latitude), cbind(BUS_Longitude, BUS_Latitude)))
#Convert to miles
final_data<- final_data %>% 
  mutate(dist =dist/1609.344)
#Round to two decimal points
final_data <- final_data %>% 
  mutate(across(dist,round,2))
#cleaning
final_data <- final_data %>% 
  mutate(bus_id=as.factor(bus_id))
```



## {data-background=1.png data-background-size=cover}

## {data-background=2.png data-background-size=cover}

## {data-background=3.png data-background-size=cover}

## {data-background=4.png data-background-size=cover}

## {data-background=5.png data-background-size=cover}

## {data-background=6.png data-background-size=cover}

## Deliverable
```{r, fig.width=10, fig.height=5}
#options(DT.fillContainer = T)
#datatable(final_data, fillContainer = T)
datatable(head(final_data, n = nrow(final_data)), options = list(pageLength = 5, scrollX = TRUE, scrollY = "300px") ) 
```

## Map of Generators 
```{r, fig.width=10, fig.height=5}
map_generators <- leaflet() %>% 
  addTiles() %>% 
  clearBounds() %>% 
  addCircleMarkers(data = final_data, lng = ~Generator_Longitude, lat = ~Generator_Latitude, popup = ~`Generation.Interconnection.Number`, color='darkblue', stroke = F, fillOpacity = 1, radius = 6, group = 'Generators') %>% 
  addLegend("bottomright", colors= "darkblue", labels="Generators", title="Legend", opacity = 1)
map_generators
```


## Map of Substations
```{r, fig.width=10, fig.height=5}
map_substations <- leaflet() %>% 
  addTiles() %>% 
  clearBounds() %>% 
  addCircleMarkers(data = final_data, lng = ~BUS_Longitude, lat = ~BUS_Latitude, popup = ~bus_id, color = 'green', stroke = F, fillOpacity = 1, radius = 6, group = 'Substations') %>% 
  addLegend("bottomright", colors= "green", labels="Substations", title="Legend",opacity = 1)
map_substations
```

## Map of Connections 
```{r, fig.width=10, fig.height=5}
final_data$dist_no_mi <- final_data$dist
final_data$dist <- paste(final_data$dist, " Mi")
map <- leaflet() %>% 
  addTiles() %>% 
  clearBounds() %>% 
  addCircleMarkers(data = final_data, lng = ~Generator_Longitude, lat = ~Generator_Latitude, popup = ~`Generation.Interconnection.Number`, color='darkblue', stroke = F, fillOpacity = 1, radius = 6, group = 'Generators') %>% 
  addCircleMarkers(data = final_data, lng = ~BUS_Longitude, lat = ~BUS_Latitude, popup = ~bus_id, color = 'green', stroke = F, fillOpacity = 1, radius = 6, group = 'Substations') %>%
  addLayersControl(overlayGroups = c('Generators', 'Substations'))

for(i in 1:nrow(final_data)){
  map <- addPolylines(map, lat = as.numeric(final_data[i, c("Generator_Latitude", "BUS_Latitude")]), 
                       lng = as.numeric(final_data[i, c("Generator_Longitude", "BUS_Longitude")]),
                       color = 'red', group = 'Connecting Lines',
                      popup = as.character(final_data[i, 'dist']))
}
map %>% addLayersControl(overlayGroups = c('Generators', 'Substations', 'Connecting Lines')) %>% 
  addLegend("bottomright", colors= c('green', 'darkblue', 'red'), labels=c('Substation', 'Generator','Distance'),title="Legend", group = c('Substations', 'Generators','Connecting Lines'),opacity= 1)
```

## Map of Connections Andrew MO 
```{r, fig.width=10, fig.height=5}
map <- leaflet() %>% 
  addTiles() %>% 
  #clearBounds() %>% 
  setView(lat = 39.96374, lng = -94.8106, zoom = 12) %>% 
  addCircleMarkers(data = final_data, lng = ~Generator_Longitude, lat = ~Generator_Latitude, popup = ~`Generation.Interconnection.Number`, color='darkblue', stroke = F, fillOpacity = 1, radius = 6, group = 'Generators') %>% 
  addCircleMarkers(data = final_data, lng = ~BUS_Longitude, lat = ~BUS_Latitude, popup = ~bus_id, color = 'green', stroke = F, fillOpacity = 1, radius = 6, group = 'Substations') %>%
  addLayersControl(overlayGroups = c('Generators', 'Substations'))

for(i in 1:nrow(final_data)){
  map <- addPolylines(map, lat = as.numeric(final_data[i, c("Generator_Latitude", "BUS_Latitude")]), 
                       lng = as.numeric(final_data[i, c("Generator_Longitude", "BUS_Longitude")]),
                       color = 'red', group = 'Connecting Lines',
                      popup = as.character(final_data[i, 'dist']))
}
map %>% addLayersControl(overlayGroups = c('Generators', 'Substations', 'Connecting Lines')) %>% 
  addLegend("bottomright", colors= c('green', 'darkblue', 'red'), labels=c('Substation', 'Generator','Distance'),title="Legend", group = c('Substations', 'Generators','Connecting Lines'),opacity= 1)
```

## Histogram of Distances Between Proposed Generators and Substations
```{r, fig.width=10, fig.height=5}
final_data %>%
  ggplot(aes(x = dist_no_mi))+
  geom_histogram(bins = 50, fill = 'royalblue') +
  scale_x_continuous(name = 'Haversine Distance (Miles)') +
  scale_y_continuous(name = 'Count') 
```

## Map of Different Energy Types
```{r, fig.width=10, fig.height=5}
# create sub tables for each type of generations
solar_gen <- final_data %>% 
  filter(`Generation.Type` == "Solar" ) #138

battery_gen <- final_data %>% 
  filter(`Generation.Type` == "Battery/Storage" ) #79

hybrid_gen <- final_data %>% 
  filter(`Generation.Type` == "Hybrid") #40

thermal_gen <- final_data %>% 
  filter(`Generation.Type` == "Thermal") #13

wind_gen <- final_data %>% 
  filter(`Generation.Type` == "Wind") #46

map_En_Type <- leaflet() %>% 
  addTiles() %>% 
  clearBounds() %>% 
  addCircleMarkers(data = solar_gen, lng = ~Generator_Longitude, lat = ~Generator_Latitude, popup = ~`Generation.Interconnection.Number`, color='orange', stroke = F, fillOpacity = 1, radius = 6, group = 'Solar') %>% 
  
  addCircleMarkers(data = battery_gen, lng = ~Generator_Longitude, lat = ~Generator_Latitude, popup = ~`Generation.Interconnection.Number`, color='black', stroke = F, fillOpacity = 1, radius = 6, group = 'Battery') %>%
  
  addCircleMarkers(data = hybrid_gen, lng = ~Generator_Longitude, lat = ~Generator_Latitude, popup = ~`Generation.Interconnection.Number`, color='green', stroke = F, fillOpacity = 1, radius = 6, group = 'Hybrid') %>% 
  
  addCircleMarkers(data = thermal_gen, lng = ~Generator_Longitude, lat = ~Generator_Latitude, popup = ~`Generation.Interconnection.Number`, color='red', stroke = F, fillOpacity = 1, radius = 6, group = 'Thermal') %>% 
  
  addCircleMarkers(data = wind_gen, lng = ~Generator_Longitude, lat = ~Generator_Latitude, popup = ~`Generation.Interconnection.Number`, color='blue', stroke = F, fillOpacity = 1, radius = 6, group = 'Wind') %>% 
  
  addLayersControl(overlayGroups = c('Solar', 'Battery','Hybrid','Thermal','Wind')) %>% 

  addLegend("bottomright", colors= c('orange', 'black', 'green', 'red', 'blue'), labels=c('Solar', 'Battery','Hybrid','Thermal', 'Wind'),title="Generation Type", group = c('Solar', 'Battery','Hybrid','Thermal','Wind'))

map_En_Type
```

## Bar Chart of Different Energy Types
```{r, fig.width=10, fig.height=5}
plot <- final_data %>%
  group_by(`Generation.Type`) %>%
  count()

ggplot(data=plot, aes(x=reorder(plot$`Generation.Type`, -plot$n), y=plot$n, fill=plot$`Generation.Type`)) +
  geom_bar(stat="identity") +
  theme(axis.text.x = element_text(angle=45, vjust=1, hjust=1)) +
  ylab("Number of Generators") +
  xlab("Generator Type") + 
  labs(fill="Generator Type") +
  geom_text(aes(label=plot$n), position=position_dodge(width=0.9), vjust=-0.25)
```


## {data-background=11.png data-background-size=cover}

## {data-background=12.png data-background-size=cover}



















